Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2024-12-11 src/tex/ms.tex
fix eqn formatting

We then determined which planets were both in the \gls{HZ} and had \gls{NUV} fluxes above $F_\mathrm{NUV, min}$.
To avoid considering short transitional phases, we require this situation to last for a minimum duration $\Delta T_\mathrm{min} \geq \var{deltaT_min}\,\SI{}{\mega\year}$.
We assigned the development of life to a random fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For the probability of a planet having detectable biosignatures, $P(\mathrm{bio})$, the UV~Threshold Hypothesis then states
\begin{equation}\label{eq:hypothesis-uv}
    H_{1} : P(\mathrm{bio}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \,\mathrm{and\, in\, HZ} \, \mathrm{for} \, \Delta t \geq \var{deltaT_min} \,\SI{}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_\mathrm{null} : P(\mathrm{bio}) = f_\mathrm{life},$
%\end{equation}
i.e., no correlation with UV flux.
% TODO: IF INFERENCE: add:
%Our choice of priors was to sample $f_\mathrm{life}$ from a log-uniform distribution between $10^{-3}$ and $1$ and $F_\mathrm{NUV, min}$ from a log-uniform distribution between $10^{1}$ and $10^{5}$.

>>>>

We then determined which planets were both in the \gls{HZ} and had \gls{NUV} fluxes above $F_\mathrm{NUV, min}$.
To avoid considering short transitional phases, we require this situation to last for a minimum duration $\Delta T_\mathrm{min} \geq \var{deltaT_min}\,\SI{}{\mega\year}$.
We assigned the development of life to a random fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For the probability of a planet having detectable biosignatures, $P(\mathrm{bio})$, the UV~Threshold Hypothesis then states
\begin{equation}\label{eq:hypothesis-uv}
    H_{1} : P(\mathrm{bio}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \\
            & \text{and in HZ for} \, \Delta t \geq \var{deltaT_min} \,\SI{}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_\mathrm{null} : P(\mathrm{bio}) = f_\mathrm{life},$
%\end{equation}
i.e., no correlation with UV flux.
% TODO: IF INFERENCE: add:
%Our choice of priors was to sample $f_\mathrm{life}$ from a log-uniform distribution between $10^{-3}$ and $1$ and $F_\mathrm{NUV, min}$ from a log-uniform distribution between $10^{1}$ and $10^{5}$.
